---
title: "Connectivity effects on plant-hummingbird interactions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(dplyr)
library(tidyr)
library(purrr)
library(glmmTMB)
library(DHARMa)
library(ggplot2)
library(GGally)
library(ggpubr)
```

**Goal**

Statistically model effects of connectivity on plant-hummingbird interactions, specifically:

  * hummingbird abundance (based on hummingbirds captured in mist nets)
  * hummingbird visitation rates to *Heliconia tortuosa* (interactions observed with trail cameras)
  * pollination success of *Heliconia tortuosa* (pollen tubes)
  * network specialization (interactions observed with trail cameras)
  
**Approach**

- Generalized linear mixed models, using the following distributions:

  * hummingbird abundance (Poisson)
  * hummingbird visitation rates to *Heliconia tortuosa* (zero-inflated Poisson)
  * pollination success of *Heliconia tortuosa* (binomial)
  * network specialization (beta)

- Include other factors thought to influence hummingbird occurrence/behavior as covariates, specifically:

  * density of *Heliconia tortuosa* (Ln calories/ha)
  * density of floral resources other than *Heliconia tortuosa* (Ln calories/ha)

- Include additional covariates depending on the response variable

  * hummingbird abundance: capture effort (net-hours)
  * hummingbird visitation rates to *Heliconia tortuosa*: number of flowers present at camera

- For hummingbird abundance and hummingbird visitation rates, analyze for all hummingbird species and for *Heliconia* specialists (Green hermits and Violet sabrewings)

# Step 1: Get functions and data

Functions
```{r}
source("code/functions/Modeling_helper_functions.R")
source("code/functions/Transform_proportion_for_betareg.R")
```

Connectivity metric, calculated in previous scripts
```{r}
#Connectivity for each site (aka "weighted patch area")
connectivity <- read.csv("data/export/for_analysis/patchMetrics_20200701.csv") %>%
  select(patch, connectivity = weighted_patch_area)
```

The following data have been used in other publications and are publicly available on Dryad. Because these datasets were collected as part of an experiment, we will only look at data before the experimental manipulation occurred (i.e., only during the 'pre' period).

Other predictor variables: https://doi.org/10.5061/dryad.jwstqjqbh
```{r}
#Density of Heliconia
heto_density <- read.csv("../hummingbird-persistence/data/export/for_analysis/Site_and_replicate_characteristics.csv") %>%
  select(year, patch, heto_calories_per_ha)

#Density of non-Heliconia
nonheto_density <- read.csv("../hummingbird-persistence/data/export/for_analysis/Percentage_calories_removed.csv") %>%
  filter(estimate_name == "high_estimate") %>% #resource availability tailored to hummingbird groups based on relative visitation rates to each plant species
  select(bird_group, year, patch, nonheto_calories_per_ha) %>%
  arrange(bird_group)
```

Hummingbird abundance, visitation rates, and plant pollination success: https://doi.org/10.5061/dryad.jwstqjqbh
```{r}
#Hummingbird abundance
captures <- read.csv("../hummingbird-persistence/data/export/for_analysis/Capture_rates.csv") %>%
  filter(exp_phase == "capture_1") %>% #'pre' period
  select(bird_group, year, patch, net_hours, num_birds) %>%
  left_join(connectivity) %>%
  left_join(heto_density) %>%
  left_join(nonheto_density) %>%
  mutate(log_heto_calories_per_ha = log(heto_calories_per_ha),
         log_nonheto_calories_per_ha = log(nonheto_calories_per_ha))

#Hummingbird visitation rates to Heliconia
heto_visits <- read.csv("../hummingbird-persistence/data/export/for_analysis/Camera_visitation_rates.csv") %>%
  filter(exp_phase == "pre") %>%
  filter(plant_species == "HETO") %>%
  select(bird_group, year, patch, plant_species, hours, flowers, sightings) %>%
  left_join(connectivity) %>%
  left_join(heto_density) %>%
  left_join(nonheto_density) %>%
  mutate(log_heto_calories_per_ha = log(heto_calories_per_ha),
         log_nonheto_calories_per_ha = log(nonheto_calories_per_ha))

#Pollination success of Heliconia
heto_pollination <- read.csv("../hummingbird-persistence/data/export/for_analysis/Pollen_tube_pollination_success.csv") %>%
  filter(exp_phase == "pre") %>%
  filter(plant_species == "HETO") %>%
  select(year, patch, starts_with("styles"), prop_with_tubes) %>%
  mutate(bird_group = "greh_visa") %>% #Add resource availability tailored to Green hermits/Violet sabrewings (primary pollinators)
  left_join(connectivity) %>%
  left_join(heto_density) %>%
  left_join(nonheto_density) %>%
  mutate(log_heto_calories_per_ha = log(heto_calories_per_ha),
         log_nonheto_calories_per_ha = log(nonheto_calories_per_ha))
```

Network metrics: https://doi.org/10.5061/dryad.70rxwdc34
```{r}
#Network specialization
network_specialization <- read.csv("../hummingbird-rewiring/data/export/for_analysis/Network_specialization_for_analysis.csv") %>%
  filter(exp_phase == "pre") %>%
  filter(sampling_method == "visitation") %>%
  filter(metric == "H2") %>%
  select(bird_group, year, patch, metric, value) %>%
  left_join(connectivity) %>%
  left_join(heto_density) %>%
  left_join(nonheto_density) %>%
  mutate(log_heto_calories_per_ha = log(heto_calories_per_ha),
         log_nonheto_calories_per_ha = log(nonheto_calories_per_ha))

#I thought I might need to transform proportion to avoid values of exactly zero or exactly one, but those values are not present in this dataset
#mutate(value_transform = transform_proportion(value)) 
```

## Step 2: Check for multicollinearity between covariates

```{r}
data_predictors <- nonheto_density %>%
  filter(bird_group == "all_spp") %>%
  left_join(heto_density) %>%
  left_join(connectivity) %>%
  mutate(log_heto_calories_per_ha = log(heto_calories_per_ha),
         log_nonheto_calories_per_ha = log(nonheto_calories_per_ha))

#Pairs plot, unlogged variables
labels <- c("Heliconia density", "Non-Heliconia density", "Connectivity")
pairs_plot <- data_predictors %>%
  select(heto_calories_per_ha, nonheto_calories_per_ha, connectivity) %>%
  GGally::ggpairs(., upper=list(continuous=wrap("cor", size = 6)), columnLabels = labels) +
   theme_bw(base_size = 14) +
   theme(strip.text = element_text(size = 12), strip.background = element_rect(fill="white"), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

pairs_plot

#Pairs plot, logged variables
log_labels <- c("Heliconia density", "Non-Heliconia density", "Connectivity")
log_pairs_plot <- data_predictors %>%
  select(log_heto_calories_per_ha, log_nonheto_calories_per_ha, connectivity) %>%
  ggpairs(., upper=list(continuous=wrap("cor", size = 6)), columnLabels = log_labels) +
   theme_bw(base_size = 14) +
   theme(strip.text = element_text(size = 12), strip.background = element_rect(fill="white"), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

log_pairs_plot

#Resource & connectivity only, with logged variables
resource_connect_labels <- c("Ln Heliconia\n density", "Ln Non-Heliconia\ndensity", "Connectivity")
resource_connect_plot <- data_predictors %>%
  select(log_heto_calories_per_ha, log_nonheto_calories_per_ha, connectivity) %>%
  GGally::ggpairs(.,
                  upper = list(continuous = wrap("cor", size = 8)),
                  lower = list(continuous = wrap("smooth")), #default seems to be lm: https://www.rdocumentation.org/packages/GGally/versions/1.5.0/topics/ggally_smooth
                  columnLabels = resource_connect_labels) +
   theme_bw(base_size = 20) +
   theme(strip.text = element_text(size = 14), strip.background = element_rect(fill="white"), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

resource_connect_plot

#Export plot
ggsave("results/figures/FigS1.png", plot = resource_connect_plot, width = 8, height = 8, units = "in", dpi = 300)
```

Pearson correlations (same values as in correlation plot)
```{r}
#These are the highest correlations
cor.test(data_predictors$connectivity, data_predictors$log_nonheto_calories_per_ha)
cor.test(data_predictors$heto_calories_per_ha, data_predictors$log_nonheto_calories_per_ha)
```

## Step 3: Fit models

Hummingbird abundance (all hummingbird species)
```{r, fig.show = 'hide', results = 'hide', echo = FALSE}
captures_all_spp <- captures %>%
  filter(bird_group == "all_spp")

m1 <- glmmTMB::glmmTMB(num_birds ~  scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_all_spp, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_all_spp, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_all_spp, na.action = na.omit, family = "nbinom1", ziformula = ~0)

m4 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_all_spp, na.action = na.omit, family = "nbinom1", ziformula = ~1, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m5 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_all_spp, na.action = na.omit, family = "nbinom2", ziformula = ~0)

m6 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_all_spp, na.action = na.omit, family = "nbinom2", ziformula = ~1, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

#Combine models
model_fitting_captures_all_spp <-  tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting_captures_all_spp %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Model 1 (Poisson)

#Check assumptions
model_fitting_captures_all_spp$dharma_plot[[1]]
model_fitting_captures_all_spp$dharma_zeroinfl_plot[[1]]
model_fitting_captures_all_spp$dharma_overdisp_plot[[1]]

#Hmm, Model 1 doesn't look great. Model 2 (ZIP), Model 3 (nbinom1), and  Model 5 (nbinom2) are next best models
model_fitting_captures_all_spp$dharma_plot[[2]]
model_fitting_captures_all_spp$dharma_zeroinfl_plot[[2]]
model_fitting_captures_all_spp$dharma_overdisp_plot[[2]]

model_fitting_captures_all_spp$dharma_plot[[3]]
model_fitting_captures_all_spp$dharma_zeroinfl_plot[[3]]
model_fitting_captures_all_spp$dharma_overdisp_plot[[3]]

model_fitting_captures_all_spp$dharma_plot[[5]]
model_fitting_captures_all_spp$dharma_zeroinfl_plot[[5]]
model_fitting_captures_all_spp$dharma_overdisp_plot[[5]]

#Model 2 (ZIP) looks best in terms of assumptions
model_captures_all_spp <- m2
```

Hummingbird abundance (*Heliconia* specialists)
```{r, fig.show = 'hide', results = 'hide', echo = FALSE}
captures_greh_visa <- captures %>%
  filter(bird_group == "greh_visa")

m1 <- glmmTMB::glmmTMB(num_birds ~  scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_greh_visa, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_greh_visa, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_greh_visa, na.action = na.omit, family = "nbinom1", ziformula = ~0)

m4 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_greh_visa, na.action = na.omit, family = "nbinom1", ziformula = ~1, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m5 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_greh_visa, na.action = na.omit, family = "nbinom2", ziformula = ~0)

m6 <- glmmTMB::glmmTMB(num_birds ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(net_hours) + (1|patch), data = captures_greh_visa, na.action = na.omit, family = "nbinom2", ziformula = ~1, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

#Combine models
model_fitting_captures_greh_visa <-  tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting_captures_greh_visa %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Model 1 (Poisson)

#Check assumptions
model_fitting_captures_greh_visa$dharma_plot[[1]]
model_fitting_captures_greh_visa$dharma_zeroinfl_plot[[1]]
model_fitting_captures_greh_visa$dharma_overdisp_plot[[1]]

model_captures_greh_visa <- m1
```

Hummingbird visitation rates to *Heliconia* (all hummingbird species)
```{r, fig.show = 'hide', results = 'hide', echo = FALSE}
heto_visits_all_spp <- heto_visits %>%
  filter(bird_group == "all_spp")

m1 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_all_spp, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_all_spp, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_all_spp, na.action = na.omit, family = "nbinom1", ziformula = ~0, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m4 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_all_spp, na.action = na.omit, family = "nbinom1", ziformula = ~1)

m5 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_all_spp, na.action = na.omit,family = "nbinom2", ziformula = ~0, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m6 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_all_spp, na.action = na.omit, family = "nbinom2", ziformula = ~1)

#Combine models
model_fitting_heto_visits_all_spp <-  tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting_heto_visits_all_spp %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Model 2 (zero-inflated Poisson)

#Check assumptions
model_fitting_captures_all_spp$dharma_plot[[2]]
model_fitting_captures_all_spp$dharma_zeroinfl_plot[[2]]
model_fitting_captures_all_spp$dharma_overdisp_plot[[2]]

model_heto_visits_all_spp <- m2
```

Hummingbird visitation rates to *Heliconia* (*Heliconia* specialists)
```{r, fig.show = 'hide', results = 'hide', echo = FALSE}
heto_visits_greh_visa <- heto_visits %>%
  filter(bird_group == "greh_visa")

m1 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_greh_visa, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_greh_visa, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_greh_visa, na.action = na.omit, family = "nbinom1", ziformula = ~0, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m4 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_greh_visa, na.action = na.omit, family = "nbinom1", ziformula = ~1)

m5 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_greh_visa, na.action = na.omit,family = "nbinom2", ziformula = ~0, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m6 <- glmmTMB::glmmTMB(sightings ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + scale(flowers) + offset(log(hours)) + (1|patch), data = heto_visits_greh_visa, na.action = na.omit, family = "nbinom2", ziformula = ~1)

#Combine models
model_fitting_heto_visits_greh_visa <-  tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting_heto_visits_greh_visa %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Model 2 (zero-inflated Poisson)

#Check assumptions
model_fitting_heto_visits_greh_visa$dharma_plot[[2]]
model_fitting_heto_visits_greh_visa$dharma_zeroinfl_plot[[2]]
model_fitting_heto_visits_greh_visa$dharma_overdisp_plot[[2]]

model_heto_visits_greh_visa <- m2
```

Pollination success of *Heliconia* (proportion of styles with at least one pollen tube)
```{r, fig.show = 'hide', results = 'hide', echo = FALSE}
m1 <- glmmTMB::glmmTMB(prop_with_tubes ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + (1|patch), data = heto_pollination, na.action = na.omit, family = "binomial", weights = styles, ziformula = ~0)

m2 <- glmmTMB::glmmTMB(prop_with_tubes ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + (1|patch), data = heto_pollination, na.action = na.omit, family = "binomial", weights = styles, ziformula = ~1)

m3 <- glmmTMB::glmmTMB(prop_with_tubes ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + (1|patch), data = heto_pollination, na.action = na.omit, family = "betabinomial", weights = styles, ziformula = ~0, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

m4 <- glmmTMB::glmmTMB(prop_with_tubes ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + (1|patch), data = heto_pollination, na.action = na.omit, family = "betabinomial", weights = styles, ziformula = ~1, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

#Combine models
model_fitting_heto_pollination <- tibble(model_name = c("m1", "m2", "m3", "m4"), model = list(m1, m2, m3, m4)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting_heto_pollination %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Model 1 (binomial)

#Check assumptions
model_fitting_heto_pollination$dharma_plot[[1]]
model_fitting_heto_pollination$dharma_zeroinfl_plot[[1]]
model_fitting_heto_pollination$dharma_overdisp_plot[[1]]

model_heto_pollination <- m1
```

Network specialization
```{r, fig.show = 'hide', results = 'hide', echo = FALSE}
model_network_specialization <- glmmTMB::glmmTMB(value ~ scale(connectivity) + scale(log_heto_calories_per_ha) + scale(log_nonheto_calories_per_ha) + (1|patch), data = network_specialization, na.action = na.omit, family = "beta_family")

#Check assumptions
simulateResiduals(model_network_specialization) %>% plot()
simulateResiduals(model_network_specialization) %>% testDispersion()
```

## Step 4: Extract and visualize results

Model summaries
```{r}
summary(model_captures_all_spp)
summary(model_captures_greh_visa) #Strong effect of connectivity on abundance of Heliconia specialists
summary(model_heto_visits_all_spp)
summary(model_heto_visits_greh_visa)
summary(model_heto_pollination)
summary(model_network_specialization) #Strong effect of connectivity on network specialization

#Combine for export
models <- tibble(model_number = c(1:6),
                  analysis = c("captures", "captures", "heto_visits", "heto_visits", "heto_pollination", "network_specialization"),
                  bird_group = c("all_spp", "greh_visa", "all_spp", "greh_visa", NA, NA),
                  model = list(model_captures_all_spp, model_captures_greh_visa, model_heto_visits_all_spp, model_heto_visits_greh_visa, model_heto_pollination, model_network_specialization))
  
results <- models %>%
  mutate(summary = map(model, summary),
         summary_tidy = map(model, broom.mixed::tidy),
         confint_wald = map(model, ~calculate_ci(., method_name = "wald")))

#Extract model summaries
results_tidy <- results %>%
  select(model_number, analysis, bird_group, summary_tidy) %>%
  unnest(c(summary_tidy))

#Extract confidence intervals
results_confint <- results %>%
  select(model_number, analysis, bird_group, confint_wald) %>%
  mutate(confint_df = map(confint_wald, as.data.frame)) %>% #CI as dataframe
  mutate(confint_df = map(confint_df, ~tibble::rownames_to_column(., var = "term"))) %>%
  unnest(cols = confint_df) %>%
  rename(lowerCI = "2.5 %", upperCI = "97.5 %") %>%
  select(-confint_wald, -Estimate)

#Back-transform coefficients and confidence intervals to data scale from model scale
results_tidy_confint <- results_tidy %>%
  left_join(results_confint) %>%
  mutate_at(vars(estimate, std.error, statistic, lowerCI, upperCI), ~round(., digits = 2)) %>%
  mutate(pvalue_round = format.pval(pv = round(p.value, 3), digits = 3, nsmall = 3, eps = 0.001)) %>%
  select(model_number:term, estimate, lowerCI, upperCI, statistic, pvalue_round, pvalue = p.value, std_error = std.error, everything())
```

Figures
```{r}
#Calculate predictions using ggeffects + add in data points (minus outlier)
predicted_values <- results %>%
  mutate(ggeffects = map(model, ~ggeffects::ggpredict(., terms = "connectivity [all]", back.transform = TRUE)))

#predicted_values$ggeffects[[1]]

#Function to make plot
make_correlation_plot <- function(ggeffects, analysis, significant){
  
  if(significant == TRUE){linetype = "solid"}
  if(significant == FALSE){linetype = "dashed"}
  if(analysis == "captures"){ylabel = "Number of birds captured"}
  if(analysis == "heto_visits"){ylabel = "Visits per hour"}
  if(analysis == "heto_pollination"){ylabel = "Pollination success"}
  if(analysis == "network_specialization"){ylabel = "Network-level specialization"}

  plot <- ggplot(data = ggeffects, aes(x = x, y = predicted)) + 
    geom_line(linewidth = 1, lty = linetype) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25) +
    theme_bw(base_size = 20) +
    theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_rect(fill="white")) + 
    scale_y_continuous(labels = scales::number_format(accuracy = 0.1, decimal.mark = '.')) +
    xlim(30000, 275000) +
    scale_x_continuous(breaks = waiver(), n.breaks = 6) +
    labs(x = "Functional connectivity", y = ylabel)

  return(plot)
  
}

#Analyses with statistically significant connectivity effect
significant_effects <- results_tidy_confint %>%
  filter(grepl("connectivity", term)) %>%
  filter(pvalue < 0.05)

results_plots <- predicted_values %>%
  mutate(significant = ifelse(model_number %in% significant_effects$model_number, TRUE, FALSE)) %>%
  mutate(predicted_plot = pmap(list(ggeffects, analysis, significant), ~make_correlation_plot(ggeffects = ..1, analysis = ..2, significant = ..3)))

# results_plots$predicted_plot
```

Combine figures

Fig. 1
```{r, fig.width=12, fig.height=12}
captures_heto_visits_plots <- results_plots %>%
  filter(analysis == "captures" | analysis == "heto_visits")

captures_heto_visits_multiplot <- ggarrange(plotlist = captures_heto_visits_plots$predicted_plot, ncol = 2, nrow = 2, labels = "AUTO", font.label = list(size = 24, face = "plain"))

captures_heto_visits_multiplot

# ggview::ggview(captures_heto_visits_multiplot, width = 12, height = 12, unit = "in")
```

Fig. 2
```{r, fig.width=6, fig.height=6}
heto_pollination_plot <- results_plots %>%
  filter(analysis == "heto_pollination") %>%
  pull(predicted_plot)

heto_pollination_plot <- heto_pollination_plot[[1]]
heto_pollination_plot

# ggview::ggview(heto_pollination_plot, width = 6, height = 6, unit = "in")
```

Fig. 3
```{r, fig.width=6, fig.height=6}
network_specialization_plot <- results_plots %>%
  filter(analysis == "network_specialization") %>%
  pull(predicted_plot)

network_specialization_plot <- network_specialization_plot[[1]]
network_specialization_plot

# ggview::ggview(network_specialization_plot, width = 6, height = 6, unit = "in")
```

## Step 5: Export results

```{r}
write.csv(results_tidy_confint, "results/tables/Model_summaries.csv")
ggsave("results/figures/Fig1.png", captures_heto_visits_multiplot, width = 12, height = 12, units = "in")
ggsave("results/figures/Fig2.png", heto_pollination_plot, width = 6, height = 6, units = "in")
ggsave("results/figures/Fig3.png", network_specialization_plot, width = 6, height = 6, units = "in")
```

